Polynomial phase estimation by phase unwrapping

### 2012-10-26 paper.tex
minor

% Template for the submission to:
%   The Annals of Probability           [aop]
%   The Annals of Applied Probability   [aap]
%   The Annals of Statistics            [aos] 
%   The Annals of Applied Statistics    [aoas]
%   Stochastic Systems                  [ssy]
%
%Author: In this template, the places where you need to add information
%        (or delete line) are indicated by {???}.  Mostly the information
%        required is obvious, but some explanations are given in lines starting
%Author:
%All other lines should be ignored.  After editing, there should be
%no instances of ??? after this line.

% use option [preprint] to remove info line at bottom
% journal options: aop,aap,aos,aoas,ssy
% natbib option: authoryear
\documentclass[aap]{imsart}

\usepackage{amsthm,amsmath,amsfonts,amssymb}
\usepackage[square,comma,numbers,sort&compress]{natbib}
%\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{units}
\usepackage{ifpdf}
\ifpdf
  \usepackage[pdftex]{graphicx}
\else
  \usepackage{graphicx}% standard graphics package for inclusion images and eps files into LaTeX document
\fi

% provide arXiv number if available:
%\arxiv{arXiv:0000.0000}

% put your definitions there:
\startlocaldefs
\newcommand{\reals}{{\mathbb R}}
\newcommand{\ints}{{\mathbb Z}}
\newcommand{\term}{\emph}
\newcommand{\var}{\operatorname{var}}
\newcommand{\covar}{\operatorname{covar}}
%\newcommand{\prob}{{\mathbb P}}
\newcommand{\prob}{\operatorname{Pr}}
\newcommand{\expect}{{\mathbb E}}
\newcommand{\dealias}{\operatorname{dealias}}
\renewcommand{\mid}{\; ; \;}
\newcommand{\fracpart}[1]{\left\langle #1 \right\rangle}
\newcommand{\sfracpart}[1]{\langle #1 \rangle}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\sabs}[1]{\vert #1 \vert}
\newcommand{\floor}[1]{{\left\lfloor #1 \right\rfloor}}
\newcommand{\ceiling}[1]{{\left\lceil #1 \right\rceil}}
\newcommand{\ceil}[1]{\lceil #1 \rceil}
\newcommand{\round}[1]{{\left\lceil #1 \right\rfloor}}
\usepackage{mathbf-abbrevs}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newcommand{\coef}{\operatorname{coef}}
\newcommand{\cubr}[1]{{\left\{ #1 \right\}}}
\newcommand{\scubr}[1]{{\{ #1 \}}}
\newcommand{\sign}[1]{\operatorname{sgn}\left( #1 \right)}
\newcommand{\bfracpart}[1]{\big\langle #1 \big\rangle}
\newcommand{\babs}[1]{\big\vert #1 \big\vert}
\endlocaldefs

\begin{document}

\begin{frontmatter}

% "Title of the paper"
\title{Polynomial phase estimation by phase unwrapping}
\runtitle{Polynomial phase estimation by phase unwrapping}

% indicate corresponding author with \corref{}
% \author{\fnms{John} \snm{Smith}\corref{}\ead[label=e1]{smith@foo.com}\thanksref{t1}}
% \thankstext{t1}{Thanks to somebody} 
% \address{line 1\\ line 2\\ printead{e1}}
% \affiliation{Some University}

\begin{aug}
\author{\fnms{Robby G.} \snm{McKilliam}\thanksref{m1}\ead[label=e1]{robby.mckilliam@unisa.edu.au}},
\author{\fnms{Barry G.} \snm{Quinn}\thanksref{m2}\ead[label=e2]{barry.quinn@mq.edu.au}},
\author{\fnms{I. Vaughan L.} \snm{Clarkson}\thanksref{m3}\ead[label=e3]{v.clarkson@uq.edu.au}},
\author{\fnms{Bill} \snm{Moran}\thanksref{m4}\ead[label=e4]{wmoran@unimelb.edu.au}},
\and
\author{\fnms{Badri N.} \snm{Vellambi}\thanksref{m1}\ead[label=e5]{badri.vellambi@unisa.edu.au}}
\runauthor{R. McKilliam et. al.}

\affiliation{University of South Australia\thanksmark{m1}, Macquarie University\thanksmark{m2}, University of Queensland\thanksmark{m3} and Melbourne University\thanksmark{m4}}

\address{R. G. McKilliam and B. N. Vellambi\\
Institute for Telecommunications Research\\
University of South Australia, Adelaide\\
SA, 5095, Australia\\
\printead{e1}\\
\phantom{E-mail:\ }\printead*{e5}}

\address{B. G. Quinn\\
Department of Statistics\\
Macquarie University, Sydney,\\
NSW, 2109, Australia\\
\printead{e3}}

\address{I. V. L. Clarkson\\
School of Information Technology \& Electrical\\
Engineering, University of Queensland,\\
Brisbane, QLD, 4072, Australia\\
\printead{e3}}

\address{B. Moran\\
Department of Electrical \& Electronic\\
Engineering, Melbourne University,\\
Melbourne, VIC, 3010, Australia\\
\printead{e4}}

\end{aug}

\begin{abstract}
Estimating the coefficients of a noisy polynomial phase signal is important in fields including radar, biology and radio communications. One approach attempts to perform polynomial regression on the phase of the signal.  This is complicated by the fact that the phase is \emph{wrapped} modulo $2\pi$ and must be \emph{unwrapped} before regression can be performed. %A recent approach suggested by the authors is to perform the unwrapping in a least squares manner.  %It was shown how the resulting estimator could be posed as a \emph{nearest lattice point problem} in a specific lattice and could be solved using existing algorithms. 
%It was shown by Monte Carlo simulation that this produces a remarkably accurate estimator.  
In this paper we consider an estimator that performs phase unwrapping in a least squares manner.  We describe the asymptotic properties of this estimator, showing that it is strongly consistent and asymptotically normally distributed. %We hypothesise that the estimator produces very near maximum likelihood performance.
\end{abstract}

%\begin{keyword}[class=AMS]
%\kwd[Primary ]{}
%\kwd{}
%\kwd[; secondary ]{}
%\end{keyword}

\begin{keyword}
\kwd{Polynomial phase signals, phase unwrapping, asymptotic statistics}
\end{keyword}

\end{frontmatter}

% AOS,AOAS: If there are supplements please fill:
% \begin{supplement}[id=suppA]
%  \sname{Supplement A}
%  \stitle{Title}
%  \slink[url]{http://lib.stat.cmu.edu/aoas/???/???}
%  \sdescription{Some text}
% \end{supplement}

@@

% %\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
% \documentclass[journal]{IEEEtran}

% \usepackage{mathbf-abbrevs}

% %\newcommand{\dealias}{\operatorname{dealias}}

% \input{defs}

% %\newcommand{\term}{\emph}
% %\renewcommand{\index}[1]{}

% %\title{Polynomial phase estimation by phase unwrapping 1: Identifiability and strong consistency}
% \title{Polynomial phase estimation by phase unwrapping}

% \author{Robby~G.~McKilliam, Barry~G.~Quinn, I.~Vaughan~L.~Clarkson, Bill~Moran and Badri~N.~Vellambi%
%     \thanks{%A preliminary version of some of this material is contained in Part 3 of Robby McKilliam's PhD thesis \cite{McKilliam2010thesis}. 
% Robby~McKilliam and Badri Vellambi are with the Institute for Telecommunications Research, The University of South Australia, SA, 5095.  Barry~Quinn is with the Department of Statistics, Macquarie University, Sydney, NSW, 2109, Australia.   Vaughan~Clarkson is with the School of Information Technology \& Electrical Engineering, The University of Queensland, QLD., 4072, Australia.  B. Moran is with the Department of Electrical Engineering and Computer
% Science, Melbourne Systems Lab, Dept of Elec \& Electronic Eng, Uni of Melbourne, Vic. 3010, Australia.}}
% % The paper headers 
% \markboth{Polynomial phase estimation by phase unwrapping}{DRAFT \today}

% % make the title area

% \begin{document} 
% \maketitle

% \begin{abstract}
% Estimating the coefficients of a noisy polynomial phase signal is important in many fields including radar, biology and radio communications. One approach attempts to perform polynomial regression on the phase of the signal.  This is complicated by the fact that the phase is \emph{wrapped} modulo $2\pi$ and must be \emph{unwrapped} before regression can be performed. %A recent approach suggested by the authors is to perform the unwrapping in a least squares manner.  %It was shown how the resulting estimator could be posed as a \emph{nearest lattice point problem} in a specific lattice and could be solved using existing algorithms. 
% %It was shown by Monte Carlo simulation that this produces a remarkably accurate estimator.  
% In this paper we consider an estimator that performs phase unwrapping in a least squares manner.  We describe the asymptotic properties of this estimator, showing that it is strongly consistent and asymptotically normally distributed. %We hypothesise that the estimator produces very near maximum likelihood performance.
% \end{abstract}

% \begin{keywords}
% Polynomial phase signals, phase unwrapping, asymptotic properties, nearest lattice point problem
% \end{keywords}

% %\bibliographystyle{unsrt}

>>>>

% % Template for the submission to:
% %   The Annals of Probability           [aop]
% %   The Annals of Applied Probability   [aap]
% %   The Annals of Statistics            [aos] 
% %   The Annals of Applied Statistics    [aoas]
% %   Stochastic Systems                  [ssy]
% %
% %Author: In this template, the places where you need to add information
% %        (or delete line) are indicated by {???}.  Mostly the information
% %        required is obvious, but some explanations are given in lines starting
% %Author:
% %All other lines should be ignored.  After editing, there should be
% %no instances of ??? after this line.

% % use option [preprint] to remove info line at bottom
% % journal options: aop,aap,aos,aoas,ssy
% % natbib option: authoryear
% \documentclass[aap]{imsart}

% \usepackage{amsthm,amsmath,amsfonts,amssymb}
% \usepackage[square,comma,numbers,sort&compress]{natbib}
% %\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
% \usepackage{units}
% \usepackage{ifpdf}
% \ifpdf
%   \usepackage[pdftex]{graphicx}
% \else
%   \usepackage{graphicx}% standard graphics package for inclusion images and eps files into LaTeX document
% \fi

% % provide arXiv number if available:
% %\arxiv{arXiv:0000.0000}

% % put your definitions there:
% \startlocaldefs
% \newcommand{\reals}{{\mathbb R}}
% \newcommand{\ints}{{\mathbb Z}}
% \newcommand{\term}{\emph}
% \newcommand{\var}{\operatorname{var}}
% \newcommand{\covar}{\operatorname{covar}}
% %\newcommand{\prob}{{\mathbb P}}
% \newcommand{\prob}{\operatorname{Pr}}
% \newcommand{\expect}{{\mathbb E}}
% \newcommand{\dealias}{\operatorname{dealias}}
% \renewcommand{\mid}{\; ; \;}
% \newcommand{\fracpart}[1]{\left\langle #1 \right\rangle}
% \newcommand{\sfracpart}[1]{\langle #1 \rangle}
% \newcommand{\abs}[1]{\left\vert #1 \right\vert}
% \newcommand{\sabs}[1]{\vert #1 \vert}
% \newcommand{\floor}[1]{{\left\lfloor #1 \right\rfloor}}
% \newcommand{\ceiling}[1]{{\left\lceil #1 \right\rceil}}
% \newcommand{\ceil}[1]{\lceil #1 \rceil}
% \newcommand{\round}[1]{{\left\lceil #1 \right\rfloor}}
% \usepackage{mathbf-abbrevs}
% \newtheorem{proposition}{Proposition}
% \newtheorem{corollary}{Corollary}
% \newtheorem{theorem}{Theorem}
% \newtheorem{lemma}{Lemma}
% \newtheorem{definition}{Definition}
% \newcommand{\coef}{\operatorname{coef}}
% \newcommand{\cubr}[1]{{\left\{ #1 \right\}}}
% \newcommand{\scubr}[1]{{\{ #1 \}}}
% \newcommand{\sign}[1]{\operatorname{sgn}\left( #1 \right)}
% \newcommand{\bfracpart}[1]{\big\langle #1 \big\rangle}
% \newcommand{\babs}[1]{\big\vert #1 \big\vert}
% \endlocaldefs

% \begin{document}

% \begin{frontmatter}

% % "Title of the paper"
% \title{Polynomial phase estimation by phase unwrapping}
% \runtitle{Polynomial phase estimation by phase unwrapping}

% % indicate corresponding author with \corref{}
% % \author{\fnms{John} \snm{Smith}\corref{}\ead[label=e1]{smith@foo.com}\thanksref{t1}}
% % \thankstext{t1}{Thanks to somebody} 
% % \address{line 1\\ line 2\\ printead{e1}}
% % \affiliation{Some University}

% \begin{aug}
% \author{\fnms{Robby G.} \snm{McKilliam}\thanksref{m1}\ead[label=e1]{robby.mckilliam@unisa.edu.au}},
% \author{\fnms{Barry G.} \snm{Quinn}\thanksref{m2}\ead[label=e2]{barry.quinn@mq.edu.au}},
% \author{\fnms{I. Vaughan L.} \snm{Clarkson}\thanksref{m3}\ead[label=e3]{v.clarkson@uq.edu.au}},
% \author{\fnms{Bill} \snm{Moran}\thanksref{m4}\ead[label=e4]{wmoran@unimelb.edu.au}},
% \and
% \author{\fnms{Badri N.} \snm{Vellambi}\thanksref{m1}\ead[label=e5]{badri.vellambi@unisa.edu.au}}
% \runauthor{R. McKilliam et. al.}

% \affiliation{University of South Australia\thanksmark{m1}, Macquarie University\thanksmark{m2}, University of Queensland\thanksmark{m3} and Melbourne University\thanksmark{m4}}

% \address{R. G. McKilliam and B. N. Vellambi\\
% Institute for Telecommunications Research\\
% University of South Australia, Adelaide\\
% SA, 5095, Australia\\
% \printead{e1}\\
% \phantom{E-mail:\ }\printead*{e5}}

% \address{B. G. Quinn\\
% Department of Statistics\\
% Macquarie University, Sydney,\\
% NSW, 2109, Australia\\
% \printead{e3}}

% \address{I. V. L. Clarkson\\
% School of Information Technology \& Electrical\\
% Engineering, University of Queensland,\\
% Brisbane, QLD, 4072, Australia\\
% \printead{e3}}

% \address{B. Moran\\
% Department of Electrical \& Electronic\\
% Engineering, Melbourne University,\\
% Melbourne, VIC, 3010, Australia\\
% \printead{e4}}

% \end{aug}

% \begin{abstract}
% Estimating the coefficients of a noisy polynomial phase signal is important in fields including radar, biology and radio communications. One approach attempts to perform polynomial regression on the phase of the signal.  This is complicated by the fact that the phase is \emph{wrapped} modulo $2\pi$ and must be \emph{unwrapped} before regression can be performed. %A recent approach suggested by the authors is to perform the unwrapping in a least squares manner.  %It was shown how the resulting estimator could be posed as a \emph{nearest lattice point problem} in a specific lattice and could be solved using existing algorithms. 
% %It was shown by Monte Carlo simulation that this produces a remarkably accurate estimator.  
% In this paper we consider an estimator that performs phase unwrapping in a least squares manner.  We describe the asymptotic properties of this estimator, showing that it is strongly consistent and asymptotically normally distributed. %We hypothesise that the estimator produces very near maximum likelihood performance.
% \end{abstract}

% %\begin{keyword}[class=AMS]
% %\kwd[Primary ]{}
% %\kwd{}
% %\kwd[; secondary ]{}
% %\end{keyword}

% \begin{keyword}
% \kwd{Polynomial phase signals, phase unwrapping, asymptotic statistics}
% \end{keyword}

% \end{frontmatter}

% % AOS,AOAS: If there are supplements please fill:
% % \begin{supplement}[id=suppA]
% %  \sname{Supplement A}
% %  \stitle{Title}
% %  \slink[url]{http://lib.stat.cmu.edu/aoas/???/???}
% %  \sdescription{Some text}
% % \end{supplement}

@@

%\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
\documentclass[journal]{IEEEtran}

\usepackage{mathbf-abbrevs}

%\newcommand{\dealias}{\operatorname{dealias}}

\input{defs}

%\newcommand{\term}{\emph}
%\renewcommand{\index}[1]{}

%\title{Polynomial phase estimation by phase unwrapping 1: Identifiability and strong consistency}
\title{Polynomial phase estimation by phase unwrapping}

\author{Robby~G.~McKilliam, Barry~G.~Quinn, I.~Vaughan~L.~Clarkson, Bill~Moran and Badri~N.~Vellambi%
    \thanks{%A preliminary version of some of this material is contained in Part 3 of Robby McKilliam's PhD thesis \cite{McKilliam2010thesis}. 
Robby~McKilliam and Badri Vellambi are with the Institute for Telecommunications Research, The University of South Australia, SA, 5095.  Barry~Quinn is with the Department of Statistics, Macquarie University, Sydney, NSW, 2109, Australia.   Vaughan~Clarkson is with the School of Information Technology \& Electrical Engineering, The University of Queensland, QLD., 4072, Australia.  B. Moran is with the Department of Electrical Engineering and Computer
Science, Melbourne Systems Lab, Dept of Elec \& Electronic Eng, Uni of Melbourne, Vic. 3010, Australia.}}
% The paper headers 
\markboth{Polynomial phase estimation by phase unwrapping}{DRAFT \today}

% make the title area

\begin{document} 
\maketitle

\begin{abstract}
Estimating the coefficients of a noisy polynomial phase signal is important in many fields including radar, biology and radio communications. One approach attempts to perform polynomial regression on the phase of the signal.  This is complicated by the fact that the phase is \emph{wrapped} modulo $2\pi$ and must be \emph{unwrapped} before regression can be performed. %A recent approach suggested by the authors is to perform the unwrapping in a least squares manner.  %It was shown how the resulting estimator could be posed as a \emph{nearest lattice point problem} in a specific lattice and could be solved using existing algorithms. 
%It was shown by Monte Carlo simulation that this produces a remarkably accurate estimator.  
In this paper we consider an estimator that performs phase unwrapping in a least squares manner.  We describe the asymptotic properties of this estimator, showing that it is strongly consistent and asymptotically normally distributed. %We hypothesise that the estimator produces very near maximum likelihood performance.
\end{abstract}

\begin{keywords}
Polynomial phase signals, phase unwrapping, asymptotic properties, nearest lattice point problem
\end{keywords}

%\bibliographystyle{unsrt}
